---
title: "Fuel vs Tyre Analysis"
output: html_notebook
---

#1. Overview
This notebook uses k-means clustering to group fuel usage to tire spend.

Problem Statement for Project-1-RJP
For a medium sized fleet of a grounds maintenance company there is a robust methodology in use for creating a fuel use projection for the coming year. However tyre costs fluctuate and previous budget projections have been inaccurate.
“Can we use clustering to provide a model of a relationship between fuel costs and tyre costs for the previous year, which could be used to improve the budget projection for future tyre costs?”
For this exercise solely focus on fuel cost and tyre cost relationship

#2. Load libraries
The Tidyverse is a collection of libraries that incudes all of the libraries that are required to complete this analysis

```{r}
# install.packages("tidyverse")

library(tidyverse)
```

This is a good time to set wd:
```{r}
setwd("C:/Users/jack.kennesion/Data-Fellowship/Clustering/Project")
```



# 3. Load Data

```{r}
ruth <- read.csv("Data2.csv")

head(ruth)

```

# 4. Explore and tansform data

Change titles
```{r}
names(ruth) <- c("Reg","Fuel","Tyre")

head(ruth)

```
# 5.Visualise data
```{r}
qplot(x = ruth$Fuel, y = ruth$Tyre,)
```
# 6. fine tuning kmeans
```{r}
kclustermax <- 10
wss <- sapply(1:kclustermax, function(k){kmeans(ruth[c("Fuel","Tyre")],k)$tot.withinss})

plot(1:kclustermax,wss, type="b", pch = 21, frame = FALSE, xlab="Number of clusters K", ylab = "Total Within Clusters sum of Squares")
```

# 7. Modelling (cllustering)

```{r}
# guess that out dataset has 3 clusers

kclusters <- 5

kmeansresult <- kmeans(ruth[c("Fuel","Tyre")], centers = kclusters)

#increase number of colu mns in c notation for increased variables

ruth$Cluster <- kmeansresult$cluster

ruth$Cluster <- as.factor(ruth$Cluster)

head(ruth)

ggplot(ruth, aes(x = ruth$Fuel, y = ruth$Tyre)) + geom_point(aes(colour = ruth$Cluster))

qplot(x = ruth$Tyre, y = ruth$Fuel, color = ruth$Cluster)

```

#8. Show K Means Values

```{r}
print(kmeansresult)
```